% WIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WIP
% Cover Letter like statement of why I want the gaming project
% Project: Playing in the Archives: Game Development with Aberdeen's Medieval Records
% Applicant: Sonke Wohler
% WIP
% 
% This document was inspired by a Template by Akash Benerjee: https://www.overleaf.com/articles/akash-banerjees-cv/qcxhvqqybqrq
% Feel free to distribute this template, but please keep the
% referal to HowToTeX.com.
% Date: May 2019
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[paper=a4,fontsize=11pt]{scrartcl} % KOMA-article class
							
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage{geometry}
	\textheight=700px                    % Saving trees ;-)
\usepackage{url}
\usepackage{sectsty}

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}			% Box to align text
\newcommand{\sepspace}{\vspace*{1em}}		% Vertical space macro

\newcommand{\MyName}[1]{ % Name
  \Huge \usefont{OT1}{phv}{b}{n} \hfill #1
  \par \normalsize \normalfont}

\newcommand{\MySlogan}[5]{ % Slogan (optional)
  \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1} 
  \sepspace
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#2}
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#3}
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#4}
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#5}
  \par \normalsize \normalfont}

%%% Document
%%% ------------------------------------------------------------
\begin{document}
  
  \MyName{S\"onke W\"ohler}
  \MySlogan{Programmer and Physics Graduate}{2A Fraser Street, AB25 3XS}{s.wohler.15@aberdeen.ac.uk}{07484 183216}{}
 % \sepspace %\sepspace
  
  \noindent
  Dear Dr William Hepburn, \\
  Dear Dr Jackson Armstrong,
  
%%% Statement
%%% ------------------------------------------------------------
  \sepspace
  
  \noindent
  I would like to apply to participate in the \textit{Playing in the Archives} Project as a game developer, specifically to the post advertised by Prof. Vasconcelos for a student of computing at the University of Aberdeen. 
  \sepspace
  
  \noindent
  When reading about the post, I must say, it was disappointing to think I would already be preoccupied with a full time position at the University for the Oil and Gas Industry. Thus far I have not been able to explore my interest in game development and the \textit{Playing in the Archives} project would be ideal in two ways; so much so that I would greatly regret not spending some of my free time and holiday on it.
  \sepspace
  
  \noindent
  On the one hand history is one of my passions, which developed, in part, out of historical computer games like the \textit{Stronghold} or \textit{Total War} series now about 15 years ago. Historical accuracy in media is one of the subjects I would have arguments with my friends about as I was growing up, as well as recently in fact. \\
  Around five years ago I started to discover Historical Fencing as a martial art and my passion for history met my talent for martial arts. This shifted my focus more towards original documentation, as historical fencing is largely based on the instructions from historical manuscripts, the earliest of which is from ca 1300. While I personally have not read many manuscripts I started reading some and started to get to know some of the mind set the people of this time might have lived by. 
  \sepspace
  
  \noindent
  On the other hand gaming is still one of my passions. I started with children's computer games when I was about two years old and they have helped me through some rather rough times. Naturally I developed an interest in how they come to be the way they are, much like my interest in physics and history. When I learned to program this understanding gradually grew, both through better understanding of computing concepts and through research into game development concepts, as well as the stories of some of my favourite games. 
  \sepspace
  
  \noindent
  Today I would say my interest is more in making games than playing them, but I have hesitated starting a personal project. The \textit{Playing in the Archives} project would offer me an opportunity to finally start such a project, but within a framework that would help me formulate ideas better. Most significantly, however, it would be a historically inspired project that would allow me to dive deeper into a time period that I want to know about and have learned something already. It is for the latter reason that I really decided to apply. \\
  As perfect as it would be for me, I even more care about getting the historical aspects of the project right. It would well and truly hurt to see such a project go to a developer who has limited interest in history, even if they have game development experience. Even if I will not work on the project, at least the successful applicant will have to be more qualified, so the project would be in good hands.
  \sepspace
  
  \noindent
  Lastly, should there be an interview, I should tell you that I am out of the country until the $30^{th}$ May, and would not be available until then.


%%% Regards
%%% ------------------------------------------------------------
  \sepspace
  
  \noindent
  Kindest Regards, \\
  S\"onke W\"ohler
  
  
  
  % ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! 
\end{document}
  % ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! 