% WIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WIP
% Cover Letter like statement of why I want the gaming project
% Project: Playing in the Archives: Game Development with Aberdeen's Medieval Records
% Applicant: Sonke Wohler
% WIP
% 
% This document was inspired by a Template by Akash Benerjee: https://www.overleaf.com/articles/akash-banerjees-cv/qcxhvqqybqrq
% Feel free to distribute this template, but please keep the
% referal to HowToTeX.com.
% Date: May 2019
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[paper=a4,fontsize=11pt]{scrartcl} % KOMA-article class
							
%%% Packages
%%% ------------------------------------------------------------

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{url}
\usepackage{sectsty}
\usepackage{enumitem}

%%% Options
%%% ------------------------------------------------------------

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers
\textheight=700px                    % Saving trees ;-)
\renewcommand\labelitemi{$\diamond$}   % different bullets for lists

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}			% Box to align text
\newcommand{\sepspace}{\vspace*{1em}}		% Vertical space macro

\newcommand{\MyName}[1]{ % Name
  \Huge \usefont{OT1}{phv}{b}{n} \hfill #1
  \par \normalsize \normalfont}

\newcommand{\MySlogan}[4]{ % Slogan (optional)
  \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1} 
  \sepspace
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#2}
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#3}
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#4}
  \par \normalsize \normalfont}

%%% Document
%%% ------------------------------------------------------------
\begin{document}
  
  \MyName{Diana Andreea Judea}
  \MySlogan{Graduate of Human Embryology}{Piata Bucuresti 4, Bl. Turn 4, Ap. 34, Oradea, Romania}{dianajudea@gmail.com}{+40 771 318 006}
  \sepspace \sepspace
 % \sepspace %\sepspace
  
  \noindent
  Dear Ms Sandra Nauth, \\
  Dear TRON,

%%% Statment Suggested
%%% ------------------------------------------------------------
  \sepspace
  
  \noindent 
  As you have suggested in our email conversation, I am applying for the
  position as a
  \href{https://tron-mainz.de/wp-content/uploads/2021/03/Research_Scientist_Biosampling.pdf}{Researcher
  in Biosampling}, which I found on glassdoor.com.  While it is not possible to
  convince you of my dexterity and talent in the laboratory on paper, allow me to
  present myself.
  \sepspace
  
  \noindent
  In my university projects in (with hands-on experience) ... I quickly
  realised that working in the lab requires dexterity and common sense, two
  things that are not easy to find in people.  I like to be concentrated, work
  as required of for the task at hand rather than on schedules.  It is very
  refreshing to work with people who are passionate and focused about their
  work.
  \sepspace
  
  \noindent
  company
  \sepspace
  
  \noindent
  Schlussteil
  \sepspace
  
  \noindent
  Looking forward to hearing from you, \\\\
  Kindest Regards,
  Diana Andreea Judea
  \sepspace
  
  \noindent
  PS: You have stated that Garman language skills are mostly required for
  written communication with the ethics committee.  For this I am quite
  confident, but otherwise I am not yet fluent in German.  Part of why I would
  like to work in Germany is to learn the language better (currently at B1).
  \sepspace

  \noindent
  PS. As mentioned in out conversation, I am not fluent in German, especially
  in spoken.  Currently my proficiency is at B1 level, lower than it used to be
  before I studied in the UK.  In written German I am more confident, so I feel
  taht correspondence with the ethics committee would not be a problem for me,
  especially long term.
  \sepspace

  \vspace*{\fill}
  
  \textbf{\underline{Contents:}}
  \begin{itemize}[noitemsep,topsep=0pt]
    \setlength\itemsep{1pt}
    \item CV
    \item Scan of University of Aberdeen Diploma
    \item Reference Contacts
  \end{itemize}
  
  \cleardoublepage
  
%%% Statment One Structure
%%% ------------------------------------------------------------
  \sepspace
  
  \noindent
  I am writting in reference to an open position as a
  \href{https://tron-mainz.de/wp-content/uploads/2021/03/Research_Scientist_Biosampling.pdf}{Researcher
  in Biosampling} as advertised on your website.
  \sepspace
  
  \noindent I started my professional education in nursing school, but wasn't
  for me because not enough science, depth, dexterity.  Hence moved on to
  opportunity at one of the best universities for Biomedical in the UK.
  \sepspace

  \noindent Courses and subjects at uni and relevant in Honours.  Mouse Model,
  Translation, Lab Work and Data Analysis was an important part of the degree.
  \sepspace
  
  \noindent I acquired complete fluency in English there, but German I am B1
  self assessed, used to be B2 before studying in the UK.  Aiming to become
  more fluent in Germany at every opportunity.  Much more confident in written
  language.
  \sepspace

  \noindent
  Laboratory Responsibilities: \\ Cryostating (old manual model)
  (better temperature), Vibratome, Solution Prep, cleanup and setup (where
  technically allowed and a little beyond), microscope (+fluorescent, self
  setup), Image Analysis (imageJ?), probe prep, electrophoresis \\ Focus on how
  quickly I picked things up and how much I had to figure things out myself. \\
  Difficult with malfunctioning equipment?  Exceptionally good slides.
  \sepspace
  
%%% Regards
%%% ------------------------------------------------------------
  \sepspace
  
  \noindent
  Looking forward to hearing from you.
  \sepspace
  
  \noindent
  Kindest Regards, \\
  Diana Andreea Judea

%%% Old Statement
%%% ------------------------------------------------------------

  \cleardoublepage

  \sepspace
  
    \noindent
    I would like to apply to the Embryogy Laboratory Technician position,
    advertised for the In-Vitro Fertilisation Clinic, reference number
    \textbf{ARU011T}. I have just completed my third year at the University of
    Aberdeen in a BSc (Hons) of Human Embryology and Developmental Biology and
    I believe this is the right time to gain more professional experience
    related to my degree, before going into my fourth year.  \sepspace
    
    %%% 
    
    \noindent The University of Aberdeen, as a whole and its IVF clinic
    specifically, have historically been at the cutting edge of scientific
    advancement and patient care, attempting to use its status in one to
    benefit the other. For myself, rather than simply being close to where I
    study, this is perhaps one of the most ideal environments to achieve a
    professional level in my skills, and perhaps grow further to eventually
    contribute on a higher level.  \sepspace
    
    %%%
    
    \noindent As a student of Human Embryology, laboratory procedures, like
    pipetting, preparing ELISAs, in vitro fertilisation of model organisms and
    maintaining cell cultures, are core skills for my degree. More than this,
    these are the aspects that I enjoy the most and wish to expand on as much
    as possible, beyond what the university can offer me. So far I have learnt
    to be precise and reliable in my nursing training, performing injections,
    taking blood and monitoring patient vitals on a daily basis. In the
    laboratory these skills based on focus and precision have proven to be
    essential for productive results, which in turn aided my understanding of
    the subjects and my ability to draw meaningful conclusions.  \sepspace
    
    %%%
    
    \noindent
    I believe, while I certainly lack professional experience, I am a capable laboratory worker with a good education and high learning motivation. This would be a great opportunity for me, and I believe I could clearly benefit the IVF team.

  
  
\end{document}
