% WIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WIP
% Cover Letter like statement of why I want the gaming project
% Project: Playing in the Archives: Game Development with Aberdeen's Medieval Records
% Applicant: Sonke Wohler
% WIP
% 
% This document was inspired by a Template by Akash Benerjee: https://www.overleaf.com/articles/akash-banerjees-cv/qcxhvqqybqrq
% Feel free to distribute this template, but please keep the
% referal to HowToTeX.com.
% Date: May 2019
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[paper=a4,fontsize=11pt]{scrartcl} % KOMA-article class
							
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage{geometry}
	\textheight=700px                    % Saving trees ;-)
\usepackage{url}
\usepackage{sectsty}

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers

%%% Macros
%%% ------------------------------------------------------------
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}			% Box to align text
\newcommand{\sepspace}{\vspace*{1em}}		% Vertical space macro

\newcommand{\MyName}[1]{ % Name
  \Huge \usefont{OT1}{phv}{b}{n} \hfill #1
  \par \normalsize \normalfont}

\newcommand{\MySlogan}[4]{ % Slogan (optional)
  \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1} 
  \sepspace
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#2}
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#3}
  \par \normalsize \usefont{OT1}{phv}{m}{n}\hfill \textit{#4}
  \par \normalsize \normalfont}

%%% Document
%%% ------------------------------------------------------------
\begin{document}
  
  \MyName{S\"onke W\"ohler}
  \MySlogan{Programmer and Physics Graduate}{2A Fraser Street, AB25 3XS}{s.wohler.15@aberdeen.ac.uk}{07484 183216}
 % \sepspace %\sepspace
  
  \noindent
  Dear Dr William Hepburn, \\
  Dr Jackson Armstrong, \\
  Prof Wamberto Vasconcelos,
  
%%% Statement
%%% ------------------------------------------------------------
  \sepspace
  
    \noindent
    I would like to apply to participate in the \textit{Playing in the Archives} project as a game developer, specifically to the post advertised by Prof Vasconcelos for a student of computing at the University of Aberdeen. In my humble opinion, the post is well cut out for me for two reasons.
    \sepspace
    
    %%% Hisory Interest
    
    \noindent
    On the one hand, history is one of my passions, which developed, in part, out of historical computer games like the \textit{Stronghold} or \textit{Total War} series, now about 15 years ago. Historical accuracy in media is one of the subjects I would have arguments with my friends about as I was growing up, as well as recently in fact. 
    \sepspace
    
    \noindent
    Around five years ago I started to discover Historical Fencing and my passion for history met my talent for martial arts. This shifted my focus more towards original documentation, as historical fencing is largely based on the instructions from historical manuscripts. In fact, the oldest known treatise is about one hundred years older than the earliest Aberdeen Burgh records. While I have not read nearly as many of these manuscripts as I would like, it has helped me gain insights into the life and mentality of the periods.
    \sepspace
    
    %%% Gaming Interest
    
    \noindent
    On the other hand gaming is still one of my passions. I started with children's computer games when I was about two years old and they have helped me through some personally rough times. Naturally I developed an interest in how they are made that I could build on with my university study, both through better understanding of computing science and through research into game development concepts.
    \sepspace
    
    \noindent
    Today I would say my interest is more in making games than playing them, but I have hesitated developing my own. The \textit{Playing in the Archives} project would offer me an opportunity to finally begin developing myself. Most significantly, however, it would be a historically inspired project that would allow me to dive deeper into a time period that I want to know about and have learned something already. It is for the latter reason that I really decided to apply. 
    \sepspace
    
    %%% Care about the Project
    
    \noindent
    As perfect as this post would be for me, even more I care about getting the historical aspects of the project right. It would well and truly hurt to see such a project go to a developer who has limited interest in history, even if they have game development experience. Should I not work on the project, at least the successful applicant will have to be more qualified, which would place the project in good hands.
    \sepspace
    
    %%% 
    
    \noindent
    Lastly, I should mention that I am out of the country until the end of May and won't be available for interview until then. I will, however, be available to work throughout the summer.


%%% Regards
%%% ------------------------------------------------------------
  \sepspace
  
  \noindent
  Kindest Regards, \\
  S\"onke W\"ohler
  
  
  
  % ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! 
\end{document}
  % ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! WIP ! 